Modeling costs and benefits of genomic wastewater surveillance

### 2023-05-16 paper/manuscript.qmd
updating manuscript

[^1]: We start with a simplified version including only a minimal set of disease states before expanding the state-space of the model to include asymptomatic, mildy symptomatic and severely symptomatic compartments

@@

where $\dot{\mathbf{S}}, \dot{\mathbf{E}}, \dot{\mathbf{P}}, \dot{\mathbf{I}}, \dot{\mathbf{R}}$ represent the time derivatives of each disease status, greek letters represent progression rates and $p_x\mathbf{m}_x$ terms represent migration flows $\mathbf{m}_x$ modulated by propensity to travel $p_x$ at disease state $x \in \{S, E, P, I, R\}$. @fig-model-diagram illustrates the model.

```{mermaid}
%%| label: fig-model-diagram
%%| fig-cap: Model diagram
%%| fig-width: 6.5
%%| fig-align: center
flowchart LR
  S --> E --> P --> I --> R
  I --> D
```

>>>>

[^1]: This model specification includes only a minimal set of disease states before expanding the state-space of the model to include asymptomatic, mildly symptomatic and severely symptomatic compartments.

@@

where $\dot{\mathbf{S}}, \dot{\mathbf{E}}, \dot{\mathbf{P}}, \dot{\mathbf{I}}, \dot{\mathbf{R}}$ represent the time derivatives of each disease status, greek letters represent progression rates and $p_x\mathbf{m}_x$ terms represent migration flows $\mathbf{m}_x$ modulated by propensity to travel $p_x$ at disease state $x \in \{S, E, P, I, R\}$.
